The paper on blockchain front-running

### 2018-09-25 frontrunning/Latex/sections/paper.tex
[frontrunning] more blue reflections

\paragraph{Design Decision \#1: Fixed Transaction Ordering.} da Silva~\etal~\cite{fixedordering2018silva} proposes an algorithm, known as Fixed Transaction Ordering and Admission (FTOA) algorithm, in the consensus protocol that enforces the order of the transactions in the mined blocks to eliminate transaction reordering by miners. \textblue{How exactly does this fix front-running?}

\paragraph{Design Decision \#2:Privacy-Preserving Blockchains.} %Market participants are concerned about revealing information on their past trades, purchases, income, or liquidity needs. Privacy is a basic human right, that being said, there are limitations to the functionality of a system designed to preserve full privacy. However other than past transactions, real-time transactions would leak information about the sender or the intention of the order that could lead to front-running attacks. 
Privacy-preserving blockchains strive (to some extent~\cite{miller2017empirical, kappos2018empirical}) to keep all details of transactions private, including participants and amounts. As an example, ZCash~\cite{hopwood2016zcash}, uses two distinct type of addresses, transparent addresses and shielded addresses. Transparent addresses work similar to Bitcoin transactions, fully transparent about the sender and receiver addresses, the amount and included data. However shielded addresses are private and do not leak any of this information. While this works for simple transactions, building similar shields for DApps is subject to on-going research~\cite{kosba2016hawk}. \textblue{How exactly does this fix front-running?}
%why this solves or makes it harder to front-run. to front run you need to know what values are there but if it is dark it's harder

>>>>

\paragraph{Design Decision \#1: Fixed Transaction Ordering.} da Silva~\etal~\cite{fixedordering2018silva} proposes an algorithm, known as Fixed Transaction Ordering and Admission (FTOA) algorithm, in the consensus protocol that enforces the order of the transactions in the mined blocks, using logical timestamps in a Byzantine setting, to eliminate transaction reordering by miners. This is a theoretical solution and will not be trivial to implement in the current Byzantine consensus protocols.

\paragraph{Design Decision \#2:Privacy-Preserving Blockchains.} Privacy-preserving blockchains strive (to some extent~\cite{miller2017empirical, kappos2018empirical}) to keep all details of transactions private, including participants and amounts. As an example, ZCash~\cite{hopwood2016zcash}, uses two distinct type of addresses, transparent addresses and shielded addresses. Transparent addresses work similar to Bitcoin transactions, fully transparent about the sender and receiver addresses, the amount and included data. However shielded addresses are private and do not leak any of this information. While this works for simple transactions, building similar shields for DApps is subject to on-going research~\cite{kosba2016hawk}. With the possibility of having private smart contracts in such a setting, it could be feasible to achieve a front-run resistance blockchain, however the functionality of the smart contracts could be limited.
